---
title: "Project Markdown INFO550"
author: "gaby blade"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# Introduction
MIMS3 is a cohort comprised of early-onset post-MI patients, and sex- and age-matched community controls designed to augment previous MIMS studies. This Rmarkdown file will analyze ambulatory heart rate variability (HRV) across different factors like age, gender and MSI (Mental Stress Ischemia). 

# Loading Data
```{r loading_data }
hrv_small = read.csv(here::here("data/hrv_small.csv")) 
```

# Table of data
```{r create_table, echo = FALSE,  child = "code/01_make_table.Rmd"}
```


# Describe table

This table shows the difference in HRV (Heart Rate Variability) by MSI (Mental Stress Ischemia) for the randomly selected patients. There are no discernible differences between the two groups (this is fake data).


# Figure of data
```{r figure_data, echo = FALSE, child = "code/02_make_fig.Rmd"}

```


# Describe figure 

The figure shows the moving average HRV LF across the 24-hr time period by MSI status. There are no discernible differences between the two groups (this is fake data).
